---
title: "Welcome To My Blog"
author: "Tobi"
date: "2023-12-06"
categories: [r4ds]
---

1.  How many rows are in `penguins`? How many columns?

    ```{r}
    #penguins
    nrow(penguins)

    ncol(penguins)

    ```

2.  What does the `bill_depth_mm` variable in the `penguins` data frame describe? Read the help for [`?penguins`](https://allisonhorst.github.io/palmerpenguins/reference/penguins.html) to find out.

    ```{r}
    # no of denoting bill depth in mm
    ```

3.  Make a scatterplot of `bill_depth_mm` vs. `bill_length_mm`. That is, make a scatterplot with `bill_depth_mm` on the y-axis and `bill_length_mm` on the x-axis. Describe the relationship between these two variables.

    ```{r}
    ggplot(penguins, aes(y=bill_depth_mm, x=bill_length_mm))+
      geom_point()

    ```

4.  What happens if you make a scatterplot of `species` vs. `bill_depth_mm`? What might be a better choice of geom?

    ```{r}
    ggplot(penguins, aes(x=bill_depth_mm, y = species))+
      geom_point()

    ```

5.  Why does the following give an error and how would you fix it?

        ggplot(data = penguins) + 
          geom_point()

    ```{r}
    ggplot(data = penguins) + 
      geom_point()
    ```

6.  What does the `na.rm` argument do in [`geom_point()`](https://ggplot2.tidyverse.org/reference/geom_point.html)? What is the default value of the argument? Create a scatterplot where you successfully use this argument set to `TRUE`.

    ```{r}
    ggplot(penguins, aes(x=bill_depth_mm,y=bill_length_mm), na.rm=TRUE)+
      geom_point()
    ```

7.  Add the following caption to the plot you made in the previous exercise: "Data come from the palmerpenguins package." Hint: Take a look at the documentation for [`labs()`](https://ggplot2.tidyverse.org/reference/labs.html).

    ```{r}

    ggplot(penguins, aes(x=bill_depth_mm,y=bill_length_mm), na.rm=TRUE)+
      geom_point() +
      labs(title = "Data come from the palmerpenguins package.")
    ```

8.  Recreate the following visualization. What aesthetic should `bill_depth_mm` be mapped to? And should it be mapped at the global level or at the geom level?

```{r}
ggplot(penguins, aes(y=body_mass_g, x=flipper_length_mm))+
  geom_point(aes(color=bill_depth_mm))+
  geom_smooth(method = "lm")

```

```{r}
ggplot(
  data = penguins,
  mapping = aes(x = flipper_length_mm, y = body_mass_g, color = island)
) +
  geom_point() +
  geom_smooth(method = "lm")
```

2\.

```{r}
ggplot(
  data = penguins,
  mapping = aes(x = flipper_length_mm, y = body_mass_g)
) +
  geom_point() +
  geom_smooth()


```

```{r}
ggplot() +
  geom_point(
    data = penguins,
    mapping = aes(x = flipper_length_mm, y = body_mass_g)
  ) +
  geom_smooth(
    data = penguins,
    mapping = aes(x = flipper_length_mm, y = body_mass_g)
  )
```

```{r}
ggplot(penguins, aes(x = sex, fill = species)) +
  geom_bar()
```

E. 2.5.5

1.  The `mpg` data frame that is bundled with the ggplot2 package contains 234 observations collected by the US Environmental Protection Agency on 38 car models. Which variables in `mpg` are categorical? Which variables are numerical? (Hint: Type [`?mpg`](https://ggplot2.tidyverse.org/reference/mpg.html) to read the documentation for the dataset.) How can you see this information when you run `mpg`?

    ```{r}
    ?mpg
    #categorical - manufacturer, model, trans, drv, fl, class

    ```

2.  ♦Make a scatterplot of `hwy` vs. `displ` using the `mpg` data frame. Next, map a third, numerical variable to `color`, then `size`, then both `color` and `size`, then `shape`. How do these aesthetics behave differently for categorical vs. numerical variables?

    ```{r}
    ggplot(mpg, aes(x=displ, y=hwy))+
      geom_point(aes(color=cty,
                     size= cty))
    ```

3.  In the scatterplot of `hwy` vs. `displ`, what happens if you map a third variable to `linewidth`?

4.  What happens if you map the same variable to multiple aesthetics?

5.  Make a scatterplot of `bill_depth_mm` vs. `bill_length_mm` and color the points by `species`. What does adding coloring by species reveal about the relationship between these two variables? What about faceting by species?

    ```{r}
    ggplot(penguins, aes(x=bill_length_mm, y=bill_depth_mm))+
      geom_point(aes(color=species))

    #shorter bill length have larger depth
    ```

6.  Why does the following yield two separate legends? How would you fix it to combine the two legends?

```{r}
ggplot(
  data = penguins,
  mapping = aes(
    x = bill_length_mm, y = bill_depth_mm, 
    color = species, shape = species
  ) 
) +
  geom_point() + labs(color = "Species", shape="Species")
  
```

```{r}

#what is the distribution in percentage of the species on the islands
ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(position = "fill")

#
ggplot(penguins, aes(x = species, fill = island)) +
  geom_bar(position = "fill")
```

```{r}
ggplot(mpg, aes(x = class)) +
  geom_bar()
ggplot(mpg, aes(x = cty, y = hwy)) +
  geom_point()
ggsave("mpg-plot.png")
```

Summary:

Got started with vissualization in ggpplot
